The Driving Forces Behind API Evolution

### 2015-05-19 thesis/paper.tex
Fixed sentence in meth

%RQ3
To allow us to answer \textbf{RQ3}, we compared our analysis and interpretation of the trends identified prior, against what was expressed by the API architect, during the interview. Success was determined by comparing the inter-rater reliability, by performing calculating Cohen's Kappa gathered data.

@@

The main thing will be:
1. Our results found that feedback loop is, a) very importnat and b) the main thing that Axis wants to improve
2. Relate to Swanson/Chapin saying the types help to budget/plan and facilitate communication between stakeholders
       [quotes re. budget/plan]:

@@

% Measures of maintenance performance are
% not meaningful except within the context
% of the organizational structure(s) upon
% which they are based.

>>>>

%RQ3
To allow us to answer \textbf{RQ3}, we compared our analysis and interpretation of the trends identified prior, against what was expressed by the API architect, during the interview. Success was determined by comparing the inter-rater reliability, by calculating Cohen's kappa \cite{cohen1968weighted} for the gathered data.

@@

The main thing will be:
1. Our results found that feedback loop is, a) very important and b) the main thing that Axis wants to improve
2. Relate to Swanson/Chapin saying the types help to budget/plan and facilitate communication between stakeholders
       [quotes re. budget/plan]:

@@

% Measures of maintenance performance are
% not meaningful except within the context
% of the organizational structure(s) upon
% which they are based. p
